```{r}
crime <- read.csv("https://raw.githubusercontent.com/asheikhz2/TTU_Zadeh/main/crime.csv", row.names = "STATE")
crime.s <- scale(crime)
```

apply k means clustering 
```{r}
km <- kmeans(crime.s, centers = 4)
table(km$cluster)
```

```{r}
subset(crime.s, km$cluster ==1)
```
```{r}
claster_means <- km$centers
rownames(claster_means) <- c("cluster_1", "cluster_2", "cluster_3", "cluster_4")
claster_means
```
cluster 1 is highly rated for violence crime and low rate of property crime 
cluster 2 is highly rated for violence and property crime
cluster 3 is highly rated for property crime and less rated in violence crime 
cluster 4 is lower rated in property and violence crime.

```{r}
km$tot.withinss
```
tot.withnss shows the wgss value of the km, the lower with in group sum of squeres value is good for clustering.

```{r}
# here we will fixed our clustering stapes using nstart= some value 
km <- kmeans(crime.s, centers = 3, nstart = 10)
table(km$cluster)
```
now if we rerun our program we dont get different results.

```{r}
# lets check the wgss value for claster 3 
km$tot.withinss
```
So this cluster 4 is batter than clauser 3. Then we will consider number of cluster 3.

```{r}
# k means doesn't have buildin scree plot function, thats why we need to build a scree plot function

plot.wgss <- function(mydata, maxc){
  wgss <- numeric(maxc)
  for(i in 1:maxc){
    km<- kmeans(mydata, centers = i, nstart = 10)
    wgss[i] <- km$tot.withinss
  }
  plot(1:maxc, wgss, type="b", xlab= "Number of cluster", ylab = "within groups sum of squares", main= "Scree Plot")
}

plot.wgss(crime.s, nrow(crime.s)-1)
```

From this Scree plot we can consider 3 cluster using Elbow method.


